---
title: "Data Summary"
author: "R. Noah Padgett"
date: "2021-08-10"
output: html_document
---

```{r setup, include=FALSE, message=F, error=F, warning=F}

source("code/load_packages.R")

```

Read in data

```{r read-data}

mydata <- readxl::read_xlsx("data/MH & COVID updated.xlsx")

mydata <- mydata[,colnames(mydata) != "filter_$"]

```


Major outcomes are the measures of mental health

* DEPR = depression
* ANX = anxiety

Scores on both of these measures in these ranges indicate clinically relevant levels of ANX/DEPR
0-7 = NORMAL; 8-10 = BORDERLINE; 11-21 CLINICALLY DEPRESSED/ANXIOUS

* AUTH = authoritarian
* BENE = benevolent



```{r}

# recode all 0's for AUTH or BENE as NA
mydata$AUTH[mydata$AUTH == 0] <- NA
mydata$BENE[mydata$BENE == 0] <- NA

mydata$Cohort = factor(mydata$COHORT, levels=1:2, labels=c("MH-COVID", "ATG"))

mydata <- mydata %>%
  group_by(Cohort) %>%
  mutate(
    BENE.z = (BENE - mean(BENE, na.rm=T))/(sd(BENE, na.rm=T))
  )


subdat <- mydata %>%
  dplyr::select(ID, Cohort, COVID, AUTH, BENE, BENE.z, AGIANX, AGIAVOID, DEPR, DEPR_DIAG, ANX, ANX_DIAG, AGI_SECURITY) 
subdat$flag = 0
i <- 1
for(i in 1:nrow(subdat)){
  subdat$flag[i] = anyNA(subdat[i,-c(1:3)])
}
subdat <- subdat %>%
  filter(flag == 0)

```

# Data Summary Statistics

```{r sumstats}
myVar <- c("AUTH", "BENE", "BENE.z", "AGIANX", "AGIAVOID", "DEPR", "DEPR_DIAG", "ANX", "ANX_DIAG", "AGI_SECURITY")

s1 <- describe(mydata[, myVar])
kable(s1, format="html", digits=2) %>%
  kable_styling(full_width = T) %>%
  scroll_box(height="400px")

s2 <- describe(subdat[, myVar])
kable(s2, format="html", digits=2) %>%
  kable_styling(full_width = T) %>%
  scroll_box(height="400px")

```

Summary stats by cohort

```{r sumstats-2}

s1 <- describeBy(mydata[, myVar],group = mydata$Cohort, mat=T)
kable(s1, format="html", digits=2) %>%
  kable_styling(full_width = T) %>%
  scroll_box(height="400px")

s2 <- describeBy(subdat[, myVar], group=subdat$Cohort, mat=T)
kable(s2, format="html", digits=2) %>%
  kable_styling(full_width = T) %>%
  scroll_box(height="400px")

```


## Visualize to help me

```{r vis}

ggplot(mydata, aes(x=Cohort, y=AUTH, color=Cohort, fill=Cohort))+
  geom_boxplot(alpha=0.5) +
  scale_color_grey()+
  scale_fill_grey()+
  theme_classic()

ggplot(mydata, aes(x=Cohort, y=BENE, color=Cohort, fill=Cohort))+
  geom_boxplot(alpha=0.5) +
  scale_color_grey()+
  scale_fill_grey()+
  theme_classic()

ggplot(mydata, aes(x=Cohort, y=BENE.z, color=Cohort, fill=Cohort))+
  geom_boxplot(alpha=0.5) +
  scale_color_grey()+
  scale_fill_grey()+
  theme_classic()

ggplot(mydata, aes(x=Cohort, y=AGIANX, color=Cohort, fill=Cohort))+
  geom_boxplot(alpha=0.5) +
  scale_color_grey()+
  scale_fill_grey()+
  theme_classic()

ggplot(mydata, aes(x=Cohort, y=AGIAVOID, color=Cohort, fill=Cohort))+
  geom_boxplot(alpha=0.5) +
  scale_color_grey()+
  scale_fill_grey()+
  theme_classic()


ggplot(mydata, aes(x=Cohort, y=DEPR, color=Cohort, fill=Cohort))+
  geom_boxplot(alpha=0.5) +
  scale_color_grey()+
  scale_fill_grey()+
  theme_classic()


ggplot(mydata, aes(x=Cohort, y=ANX, color=Cohort, fill=Cohort))+
  geom_boxplot(alpha=0.5) +
  scale_color_grey()+
  scale_fill_grey()+
  theme_classic()

```


# Missing Data


```{r miss-data-1}

miss.patt <- md.pattern(mydata, plot = T,rotate.names = T)

kable(miss.patt, format="html") %>%
  kable_styling(full_width = T) %>%
  scroll_box(height=500)


gather(mydata) %>%
    group_by(key) %>%
    summarize(prop_na = mean(is.na(value))) %>%
    ggplot(mapping = aes(x = key, y = prop_na)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(limits = c(0,1)) +
    theme_bw() + 
    theme(
      legend.key = element_blank(), 
      axis.text.x = element_text(
                       angle = 90, 
                       hjust = 1, vjust = .05))


vis_miss(mydata)
```


## Handling missing data


```{r miss-dat-2, eval=F}

## examine the number of missing cases for each variable
missing.indicator <- data.frame(is.na(mydata))
propMissing <- apply(missing.indicator,2,mean) # Vector of missininess

## create dummy missing value indicators
names(missing.indicator)[propMissing>0] <- paste(names(mydata)[propMissing>0],"NA",sep="")
## convert dummy missing indicators from logical to numeric variables
for (var in 1:ncol(missing.indicator)){
  missing.indicator[,var] <- as.numeric(missing.indicator[,var]) 
} ## End loop

## merge covariate names with missing indicator names
mydata <- cbind(mydata,missing.indicator[,propMissing>0])

## show percentage missing
print(round(propMissing,3))

## impute separately for each Cohort
# create storage
long.imputation <- c()
imputation <- list()
## loop through Divisions
for(group in c("MH-COVID", "ATG")) {
  
  ## creates a list of predictors of missing data with a mininum correlation of 0.05
  ## and at least 50% of useful data
  predictor.selection <- quickpred(
    subset(mydata,Cohort==group), mincor=0.1, minpuc=0.1,method='pearson',exclude=c("ID", "Finished", "MO_CVD", "MAJOR", "DATE_COVID")
  ) ## Creates prediction matrix more simply
  #impute variables by from least missing to most missing
  #Using multiple imputation by chained equations
  #with predictive mean matching as the univariate imputation method
  imputation[[group]] <- mice::mice(
    subset(mydata,Cohort==group), m=5,method = "pmm",
    visitSequence="monotone",
    predictorMatrix = predictor.selection)
  
  #extract stacked data files
  if(group == "MH-COVID"){
    long.imputation = rbind(long.imputation,complete(imputation[[group]], action="long",include=T))
  }
  if(group == "ATG"){
    long.imputation = rbind(long.imputation,complete(imputation[[group]], action="long"))
  }
  
  
} ## finish loop for Imputation

## extract a single imputation dataset for use in this project
imp_dat <- subset(long.imputation, subset=.imp==1)

# save imputated datasets
save(long.imputation, imp_dat, imputation, file = "data/imp_dat.RData")

```


