---
title: "Research Question 3"
subtitle: "AtG and Depression and Anxiety Scores" 
author: "R. Noah Padgett"
date: "2021-08-13"
output: html_document
---

```
Research Question 3:

Do higher levels of anxious or avoidant attachment style to God relate to higher scores of depression or anxiety in cohort 1 or 2?
```


```{r setup, include=FALSE, message=F, error=F, warning=F}

source("code/load_packages.R")
options(digits=3)
```

Read in data

```{r read-data}
# Load imputed data
load("data/imp_dat.RData")
imp_dat_c1 <- imputation[[1]]
imp_dat_c2 <- imputation[[2]]
imp_dat_mids <- rbind(imp_dat_c1, imp_dat_c2)

mydata <- readxl::read_xlsx("data/MH & COVID updated.xlsx")

mydata <- mydata[,colnames(mydata) != "filter_$"]

# recoding to correct for errors
# recode all 0's for AUTH or BENE as NA
mydata$AUTH[mydata$AUTH == 0] <- NA
mydata$BENE[mydata$BENE == 0] <- NA

mydata <- mydata %>%
  group_by(COHORT) %>%
  mutate(
    BENE.z = (BENE - mean(BENE, na.rm=T))/(sd(BENE, na.rm=T))
  )

myVar <- c("COHORT","COVID", "AUTH", "BENE","BENE.z",  "AGIANX", "AGIAVOID", "DEPR", "DEPR_DIAG", "ANX", "ANX_DIAG", "AGI_SECURITY")

subdat <- mydata %>%
  dplyr::select(ID, COHORT, COVID, AUTH, BENE, BENE.z, AGIANX, AGIAVOID, DEPR, DEPR_DIAG, ANX, ANX_DIAG, AGI_SECURITY) 
subdat$flag = 0
i <- 1
for(i in 1:nrow(subdat)){
  subdat$flag[i] = anyNA(subdat[i,-c(1:3)])
}
subdat <- subdat %>%
  filter(flag == 0)


subdat$Cohort = factor(subdat$COHORT, levels=1:2, labels=c("MH-COVID", "ATG"))


```


# Approach 1 - Listwise Deletion

Missing data are listwise deleted - using all cases with complete data on all variables of interest.

```{r}

GGally::ggpairs(
  subdat,  columns = c("DEPR", "ANX", "AGIANX", "AGIAVOID"),
  mapping = ggplot2::aes(colour=Cohort, alpha=0.75))

```

## Cohort 1

### Depression Scores

```{r}

cor.test(~DEPR + AGIANX, data=filter(subdat, COHORT==1))
cor.test(~DEPR + AGIAVOID, data=filter(subdat, COHORT==1))
```

### Anxiety Scores

```{r}

cor.test(~ANX + AGIANX, data=filter(subdat, COHORT==1))
cor.test(~ANX + AGIAVOID, data=filter(subdat, COHORT==1))
```


## Cohort 2

### Depression Scores

```{r}

cor.test(~DEPR + AGIANX, data=filter(subdat, COHORT==2))
cor.test(~DEPR + AGIAVOID, data=filter(subdat, COHORT==2))
```

### Anxiety Scores

```{r}

cor.test(~ANX + AGIANX, data=filter(subdat, COHORT==2))
cor.test(~ANX + AGIAVOID, data=filter(subdat, COHORT==2))
```



# Approach 2 - Single Complete Imputation

A single complete dataset is used

```{r}

GGally::ggpairs(
  imp_dat,  columns = c("DEPR", "ANX", "AGIANX", "AGIAVOID"),
  mapping = ggplot2::aes(colour=Cohort, alpha=0.75))

```

## Cohort 1

### Depression Scores

```{r}

cor.test(~DEPR + AGIANX, data=filter(imp_dat, COHORT==1))
cor.test(~DEPR + AGIAVOID, data=filter(imp_dat, COHORT==1))
```

### Anxiety Scores

```{r}

cor.test(~ANX + AGIANX, data=filter(imp_dat, COHORT==1))
cor.test(~ANX + AGIAVOID, data=filter(imp_dat, COHORT==1))
```


## Cohort 2

### Depression Scores

```{r}

cor.test(~DEPR + AGIANX, data=filter(imp_dat, COHORT==2))
cor.test(~DEPR + AGIAVOID, data=filter(imp_dat, COHORT==2))
```

### Anxiety Scores

```{r}

cor.test(~ANX + AGIANX, data=filter(imp_dat, COHORT==2))
cor.test(~ANX + AGIAVOID, data=filter(imp_dat, COHORT==2))
```


# Approach 3 - Full Imputation Method

## Cohort 1

### Depression Scores

```{r}
c1 <- with(
  imp_dat_c1,
  lm(scale(DEPR)~ scale(AGIANX))
)
pool(c1)
summary(D1(c1))
c1 <- with(
  imp_dat_c1,
  lm(scale(DEPR)~ scale(AGIAVOID))
)
pool(c1)
summary(D1(c1))

```

### Anxiety Scores

```{r}
c1 <- with(
  imp_dat_c1,
  lm(scale(DEPR)~ scale(AGIANX))
)
pool(c1)
summary(D1(c1))
c1 <- with(
  imp_dat_c1,
  lm(scale(DEPR)~ scale(AGIAVOID))
)
pool(c1)
summary(D1(c1))

```

## Cohort 2

### Depression Scores

```{r}
c1 <- with(
  imp_dat_c2,
  lm(scale(DEPR)~ scale(AGIANX))
)
pool(c1)
summary(D1(c1))
c1 <- with(
  imp_dat_c2,
  lm(scale(DEPR)~ scale(AGIAVOID))
)
pool(c1)
summary(D1(c1))

```

### Anxiety Scores

```{r}
c1 <- with(
  imp_dat_c2,
  lm(scale(DEPR)~ scale(AGIANX))
)
pool(c1)
summary(D1(c1))
c1 <- with(
  imp_dat_c2,
  lm(scale(DEPR)~ scale(AGIAVOID))
)
pool(c1)
summary(D1(c1))

```

